### 2022-01-17 src-latex/parts/60-results.tex
adds metrics for the 5th (last) bert-pretrained run

\begin{table}[h!]
\centering
\caption{NER performances at entry-level for SpaCy NER, CamemBERT and CamemBERT-pretrained when fine-tuned with an increasing number of examples.}
\begin{tabular}{llrrrrrrrr}
       & Number of training examples &  49   &  99   &  199  &  398  &  796  &  1593 &  3186 &  6373 \\
       & \% & 0.8   & 1.6   & 3.1   & 6.2   & 12.5  & 25.0  & 50.0  & 100.0 \\
\midrule\bottomrule
\multirow{3}{*}{\rotatebox{90}{F1 score}} & Camembert &  89.5 &  90.5 &  92.7 &  93.3 &  \textbf{94.1} &  \textbf{94.9} &  \textbf{94.6} &  \textbf{95.1} \\
       & Camembert-pretrained &  \textbf{92.4} &  \textbf{92.9} & \textbf{93.7} &  \textbf{93.8} &  93.8 &  94.0 &  \textbf{94.6} &  94.4 \\
       & SpaCy NER &  87.0 &  89.0 &  90.3 &  91.9 &  92.1 &  92.8 &  93.2 &  93.5 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Precision}} & Camembert &  87.4 &  88.7 &  91.5 &  92.7 &  93.3 &  94.9 &  93.9 &  95.1 \\
       & Camembert-pretrained &  91.2 &  91.9 &  92.9 &  93.0 &  93.0 &  93.2 &  94.2 &  93.9 \\
       & SpaCy NER &  85.6 &  87.7 &  90.0 &  92.0 &  92.4 &  92.8 &  93.1 &  93.7 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Recall}} & Camembert &  91.6 &  92.5 &  93.9 &  93.9 &  94.9 &  94.9 &  95.4 &  95.1 \\
       & Camembert-pretrained &  93.7 &  94.0 &  94.4 &  94.7 &  94.6 &  94.8 &  95.0 &  94.9 \\
       & SpaCy NER &  88.6 &  90.4 &  90.7 &  91.7 &  91.9 &  92.8 &  93.3 &  93.4 \\
\end{tabular}
\label{tab:experiment-1-models-performances}
\end{table}

>>>>

\begin{table}[h!]
\centering
\caption{NER performances at entry-level for SpaCy NER, CamemBERT and CamemBERT-pretrained when fine-tuned with an increasing number of examples.}
\begin{tabular}{llrrrrrrrr}
       & Number of training examples &  49   &  99   &  199  &  398  &  796  &  1593 &  3186 &  6373 \\
       & \% & 0.8   & 1.6   & 3.1   & 6.2   & 12.5  & 25.0  & 50.0  & 100.0 \\
\midrule\bottomrule
\multirow{3}{*}{\rotatebox{90}{F1 score}} & Camembert &  89.5 &  90.5 &  92.7 &  93.3 &  \textbf{94.1} &  \textbf{94.9} &  \textbf{94.6} &  \textbf{95.1} \\
       & Camembert-pretrained &  \textbf{92.2} &  \textbf{92.9} &  \textbf{93.6} &  \textbf{93.8} &  93.8 &  94.1 &  \textbf{94.6} &  94.4 \\
       & SpaCy NER &  87.0 &  89.0 &  90.3 &  91.9 &  92.1 &  92.8 &  93.2 &  93.5 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Precision}} & Camembert &  87.4 &  88.7 &  91.5 &  92.7 &  93.3 &  94.9 &  93.9 &  95.1 \\
       & Camembert-pretrained &  90.8 &  91.8 &  92.9 &  93.0 &  93.0 &  93.4 &  94.1 &  93.9 \\
       & SpaCy NER &  85.6 &  87.7 &  90.0 &  92.0 &  92.4 &  92.8 &  93.1 &  93.7 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Recall}} & Camembert &  91.6 &  92.5 &  93.9 &  93.9 &  94.9 &  94.9 &  95.4 &  95.1 \\
       & Camembert-pretrained &  93.6 &  94.0 &  94.4 &  94.6 &  94.6 &  94.8 &  95.0 &  94.9 \\
       & SpaCy NER &  88.6 &  90.4 &  90.7 &  91.7 &  91.9 &  92.8 &  93.3 &  93.4 \\
\end{tabular}
\label{tab:experiment-1-models-performances}
\end{table}
